### 2016-10-18 methodsPaper/tex/results.tex
vary NTM paragraph
more results

%% We used the National Household Transportation Survey to estimate the
%% mean walk and cycle times for individuals that live in metropolitan
%% areas for each of seven states (CA, TX, NY, FL, VA, NC and AZ)
%% \cite{NHTS}.  These states were selected becaused they had sufficient
%% sample size for reasonable estimates of age-sex specific
%% travel-related walking and cycling means, Figure \ref{meanMatrices}.

%% \begin{figure}[t]
%%   \centerline{\includegraphics[width=\textwidth]{./figures/fig3.pdf}}
%%     \caption{Mean travel time by mode (walking/cycling) for each of
%%       seven states.  National means are displayed on the
%%       right.}\label{meanMatrices}
%% \end{figure}

%% Of these seven states one was found to show active transport behavior
%% that, if adopted nation-wide, would avert 75-100,000 DALYs overall.
%% Values for national disease-specific DALYs were found using the CDC
%% Wonder database \cite{CDCWonder}.  California stood out among the
%% estimates for national DALYs averted.  Most of the decrease in DALYs
%% is due to prevention of dementia in the oldest age group, $80+$ years
%% old.  California exhibits much greater walking and cycling means in
%% this age group than the national average. In particular we see the
%% cycling mean We also see prevention of depression and diabetes in the
%% middle age groups due to increased active transport time.

>>>>

Running the model to compare baseline to low and high scenarios produced estimates of X change in the disease burden (1,000s DALYs) for our US population subset. We then varied the mean non-travel activity time and active travel time to observe how this chaged results (\ref{fig:currentFig1}). We observe the most dramatic responses in disease burden estimates to changes in active travel time when non-travel activity times are lowest. This result is consistent with the non-linear dose-response curve for physical activity and several health outcomes. The total health benefit of increased active travel time (high scenario) varies from X to Y with changing mean non-travel activity time (0 to 25 minutes).
